Solar jet observed at the limb in SDO/SST

### 2016-07-28 paper/ms_temp_paper.tex

>>>>

% will need to rewrite this at a later date
This particular feature, as has already been mentioned, has two events in which material is accelerated upwards into the solar atmosphere.
An examination of the dopplergrams reveals little in the way of rotational behaviour, however the second event demonstrates a characteristic division of red and blue.
